\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[black]{classic}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\firstname{Prateek}
\familyname{\mbox{Agarwal}}
\title{\small Ruby $\star$ Python $\star$ Git $\star$ Cartooning}
\phone{+1 (512) 698-3649}
\email{prat0318 @ cs.utexas.edu}
\homepage{http://prat0318.github.io}
\social[linkedin]{http://linkedin.com/in/prat0318}
\social[github]{http://github.com/prat0318}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% command and color used in this document, independently from moderncv 
\definecolor{see}{rgb}{0.5,0.5,0.5}% for web links
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}% for text subscripts
\renewcommand{\labelitemi}{$\circ$}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace*{-1cm}

\section{\textsc{Qualification Summary}}
		\cvitem{\textbullet}{Competent at managing responsibilities in a high-volume atmosphere}
		\cvitem{\textbullet}{Hard worker, quick learner, and ability to assume responsibility}

\section{\textsc{Technical Skills}}
		\cvitem{\textbullet}{\textbf{Programming Languages}: Ruby, Python, Java, C++, Javascript, PHP}
		\cvitem{\textbullet}{\textbf{Web Frameworks}: Sinatra, Django, Rails, Apache}
		\cvitem{\textbullet}{\textbf{Databases}: MySQL, PostgreSQL, IBM Informix, IBM DB2}

\section{\textsc{Github Projects}}
		\cvitem{\textbullet}{\textbf{\href{http://github.com/prat0318/2048-tetris}{prat0318/2048-tetris}} - Live at {\color{see} \href{http://2048-tetris.com}{2048-tetris.com}}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Wrote a Tetris variant of 2048 game, 1M+ unique visits\item Made it to the front page of Hacker News for a day(~150 pts), mentioned in TechCrunch.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{\href{http://github.com/prat0318/gitator}{prat0318/gitator}} - Live at {\color{see} \href{http://gitator.com}{Gitator.com}}}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Finds relevant repositories based on an user's GitHub profile.\item Written in Ruby on Sinatra, designed in Bootstrap.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}
		\cvitem{\textbullet}{\textbf{\href{http://github.com/prat0318/json\_resume}{prat0318/json\_resume}} - Convert JSON data to pretty resumes in .html, .tex, .md}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Static personal page and resume design using Mustache.\item Current resume is generated using json\_resume.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}

\section{\textsc{Professional Experience}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
		\cventry{Sept. 2013 - Jan. 2014}{Graduate Research Assistant}{CTR, UT Austin}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Developed a common web interface {\color{see} \url{http://unitydatabase.com}} to search through different datasets and output aggregate results and ensuring easy pluggability of new datasets.	
				\item Technologies got to work on:
				Python, Django, South, PostgreSQL
				\end{itemize}
			}
		}
		\cventry{Apr. 2013 - Jul. 2013}{SDE II (Software Development Engineer II)}{Flipkart}{India}{}{
			{\footnotesize 
				\begin{itemize}
				\item Wrote a ruby gem \textit{Morsel} to traverse through active record trees to purge old records. It helped in limiting the production database size and keeping the data clean.	
				\end{itemize}
			}
		}
		\cventry{Jun. 2011 - Mar. 2013}{Software Development Engineer}{Flipkart}{India}{}{
			{\footnotesize 
				\begin{itemize}
				\item Was part of a team which developed the warehouse module in RoR framework from scratch. It now scales to around 10X as compared to the ERP system existed.\item Designed warehouse stock snapshots and stock ledger framework using Pig scripts to make the supply chain system legally compliant.	
				\item Technologies got to work on:
				Ruby, Java, Pig, Active Records, MySQL
				\end{itemize}
			}
		}
		\cventry{Jul. 2009 - Jun. 2011}{Software Engineer}{IBM Software Labs}{India}{}{
			{\footnotesize 
				\begin{itemize}
				\item Handled high priority issues for JDBC client driver for IBM Informix database.\item Was awarded Smart CADian award for resolving an obscure deadlock situation, making Informix JDBC driver more robust.	
				\item Technologies got to work on:
				Java, IBM Informix, IBM DB2
				\end{itemize}
			}
		}

\section{\textsc{Other Projects}}
		\cvitem{\textbullet}{Designed product \textit{Omerta}, a multi-user chat room application in j2me using Sun Wireless Toolkit platform.}
		\vspace*{-0.15cm}
		\cvitem{}{
			{\footnotesize 
				\begin{itemize}
				\item Was awarded 1$^{st}$ position for the product in {\color{see} \href{http://www.ecell-iitkgp.org/envision.php}{Envision}}, Product Innovation Contest, IIT KGP.\item Was awarded 1$^{st}$ position for the product in Javawise, J2ME s/w Development Contest at IIT Kharagpur, 2008 and 2009 continuously.	
				\end{itemize}
			}
		}
		\vspace*{-0.5cm}

\section{\textsc{Education}}
%    \cventry{years}{degree/job title}{institution/employer}{localization}{grade}{description}
\cventry{2015}{Master of Science, Computer Science}{University of Texas at Austin}{}{GPA: 3.33/4}{}
\cventry{2009}{Bachelor of Technology (Hons.), Computer Science}{Indian Insitute of Technology, Kharagpur (IN)}{}{GPA: 8.91/10}{}

\section{\textsc{Academic Achievements}}
		% \cvitem{LHS}{RHS}
		\cvitem{\textbullet}{Was among the top 5\% in the institute merit list of the undergraduate batch at IIT Kharagpur.}
		% \cvitem{LHS}{RHS}
		\cvitem{\textbullet}{Secured 383rd Rank in IIT-JEE 2005, an exam conducted by Indian Institute of Technology(s).}

\section{\textsc{Graduate courses taken}}
		\cvlistdoubleitem
		{\href{http://www.cs.utexas.edu/users/lorenzo/corsi/cs380d/13F/}{Distributed Computing}}{\href{http://www.cs.utexas.edu/users/dsb/cs392f}{Feature Oriented Programming}}	
		\cvlistdoubleitem
		{\href{http://www.cs.utexas.edu/~pingali/CS395T/2013fa}{Multicore Programming}}{\href{http://www.cs.utexas.edu/users/dsb/cs386d/}{Database Systems}}	
		\cvlistdoubleitem
		{\href{}{Engineering Programming Languages}}{\href{http://www.cs.utexas.edu/users/vl/teaching/388L}{Introduction to Mathematical Logic}}	


\section{\textsc{Research Experience}}
		\cventry{Jul. 2008 - May 2009}{Undergraduate project}{Sanyog Lab, IIT Kharagpur}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Designing and Formal modelling of embedded systems for project Sanyog.\item Skills Developed: Low level system design, theorem verification using Prolog and Coq	
				\end{itemize}
			}
		}
		\cventry{May 2008 - Jun. 2008}{Summer Intern}{Network Systems Lab, IIT Kharagpur}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Design and simulation of currently published Pull-based Freshness Schemes in C++.	
				\end{itemize}
			}
		}
		\cventry{May 2007 - Jun. 2007}{Summer Intern}{Telemedicine Lab, IIT Kharagpur}{}{}{
			{\footnotesize 
				\begin{itemize}
				\item Web based medical image browsing and annotation tools for PDA devices in .NET platform.	
				\end{itemize}
			}
		}

\section{\textsc{Patents}}
		\cvitem{US Patent 5,146,634}{\textit{\href{}{Three zone bed cover with an inflatable human form.}}, issued September 15, 1992.}

\section{\textsc{Publications}}
		\cvitem{\textbullet}{Michael Douglas, Marcelo Disconzi, \textit{\href{}{On the boundedness of ective potentials arising from string compactifications}} arXiv: 1206.1885, June 2012}

\section{\textsc{Memberships}}
		\cvitem{\textbullet}{Member of the American Mathematical Society, 2008-present}

\section{\textsc{Extra Curricular Awards}}
		\cvitem{\textbullet}{Was awarded 2$^{nd}$ position in Bionetics, Coding Event, Genesis 09 at IIT Kharagpur.}
		\cvitem{\textbullet}{Microsoft Student Partner of IIT Kharagpur from the period July 08 – June 09.}

\end{document}
%% end of file `page.tex'.

